---
title: "R Notebook"
output: html_notebook
---

Interested in the impact of sleep deprivation on reaction time, Belenky et al. (2003) enlisted 18 subjects in a study. The subjects got a regular night’s sleep on “day 0” of the study, and were then restricted to 3 hours of sleep per night for the next 9 days. Each day, researchers recorded the subjects’ reaction times (in ms) on a series of tests. The results are provided in the sleepstudy dataset in the lme4 package.

Exercise 15.3 (Hierarchical data) The sleepstudy data is hierarchical. Draw a diagram in the spirit of Figure 15.8 that captures the hierarchical framework. Think: What are the “groups?”


```{r}
library(lme4)
library(ggplot2)
```

```{r}
dfStudy = lme4::sleepstudy
```

Los grupos son las personas, y quiero ver como cambia la reaccion en ms segun el dia por cada persona.

```{r}
ggplot(dfStudy,aes(Days, Reaction) ) +
  geom_point(aes(color=Subject)) +
  geom_smooth(method='lm') 
  labs(x = "flipper_length_mm", y = "body_mass_g")
```
It makes the incorrect assumption that reaction times vary equally for all participants. 
It makes the assumption that no information can be added by differentiating beetwen subjects.


```{r}
ggplot(dfStudy,aes(Days, Reaction, color=Subject) ) +
  geom_point(aes(color=Subject)) +
  geom_smooth(method='lm') 
  labs(x = "flipper_length_mm", y = "body_mass_g")
```

No pooling has more variability and it can be less robust when there are many groups and a some groups with few data.
